Discrete target distribution examples

### 2020-10-01 src/s_discrete.Rmd
started work on ml comparison

---
title: "R Notebook"
output: html_notebook
---

@@

P0 <- f_construct_random_matrix(20, rep(1, 20))
P1 <- f_construct_random_matrix(20, rep(1, 20))

saveRDS(list(P0=P0, P1=P1), "../data/discrete_higherd_matrices.rds")
# show first few stationary frequencies for the chains
g <- f_generate_four(100000, P0, P1, 1) %>% 
  as.data.frame() %>% 
  rename(chain_1=V1, chain_2=V2, chain_3=V3, chain_4=V4) %>% 
  mutate(iter=seq_along(chain_1)) %>% 
  melt(id.vars="iter") %>% 
  group_by(variable) %>% 
  summarise("1"=mean(value==1),
            "2"=mean(value==2),
            "3"=mean(value==3),
            "4"=mean(value==4)) %>% 
  pivot_longer(cols="1":"4") %>% 
  ggplot(aes(x=as.factor(name), fill=as.factor(variable), y=value)) +
  geom_col(position = position_dodge()) +
  xlab("State") +
  ylab("Frequency") +
  scale_fill_brewer("Chain", palette = "Dark2") +
  theme(axis.text = element_text(colour="black", size=16),
        axis.title = element_text(colour="black", size=16),
        strip.text.y = element_text(colour="black", size=16),
        title = element_text(colour="black", size=16),
        legend.text = element_text(colour="black", size=16))
ggsave("../output/discrete_stationary_higherd.pdf", g, width = 10, height = 6)
```

>>>>

---
title: "Discrete target distribution examples"
output: html_notebook
---

@@

# P0 <- f_construct_random_matrix(20, rep(1, 20))
# P1 <- f_construct_random_matrix(20, rep(1, 20))

saveRDS(list(P0=P0, P1=P1), "../data/discrete_higherd_matrices.rds")
temp <- readRDS("../data/discrete_higherd_matrices.rds")
P0 <- temp$P0
P1 <- temp$P1
# show first few stationary frequencies for the chains
g <- f_generate_four(100000, P0, P1, 1) %>% 
  as.data.frame() %>% 
  rename(chain_1=V1, chain_2=V2, chain_3=V3, chain_4=V4) %>% 
  mutate(iter=seq_along(chain_1)) %>% 
  melt(id.vars="iter") %>% 
  group_by(variable) %>% 
  summarise("1"=mean(value==1),
            "2"=mean(value==2),
            "3"=mean(value==3),
            "4"=mean(value==4)) %>% 
  pivot_longer(cols="1":"4") %>% 
  mutate(variable=if_else(variable=="chain_1", "1", if_else(variable=="chain_2", "2", if_else(variable=="chain_3", "3", "4")))) %>% 
  ggplot(aes(x=as.factor(name), fill=as.factor(variable), y=value)) +
  geom_col(position = position_dodge()) +
  xlab("State") +
  ylab("Frequency") +
  scale_fill_brewer("Chain", palette = "Dark2") +
  theme(axis.text = element_text(colour="black", size=16),
        axis.title = element_text(colour="black", size=16),
        strip.text.y = element_text(colour="black", size=16),
        title = element_text(colour="black", size=16),
        legend.text = element_text(colour="black", size=16))
ggsave("../output/discrete_stationary_higherd.pdf", g, width = 10, height = 6)
```
